Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2017-04-04 paperIEEE.tex
Fixup svn merge fus
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@60 db7c848b-7755-4df2-b763-8796797afa52

% The publisher's ID mark at the bottom of the page is less important with
% Computer Society journal papers as those publications place the marks
% outside of the main text columns and, therefore, unlike regular IEEE
% journals, the available text space is not reduced by their presence.
% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
% or like this to get the Computer Society new two part style.
%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2015 IEEE}%
%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark (Computer Society jorunal
% papers don't need this extra clearance.)

@@

% biography section
%
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/stefan}}]{Stefan
Eilemann} Stefan is the technical manager of the Visualization Team in the Blue
Brain Project. His work involves working towards large-scale visualization for
Exascale simulations; interactive integration of simulation, analysis and
visualization as well as flexible frameworks for data sharing and dynamic
allocation of heterogenous resources. He is the CEO and founder of Eyescale and
also the lead developer of the \textsf{Equalizer} parallel rendering framework.
He has worked in SGI's Advanced Graphics Division as the technical lead of
OpenGL Multipipe SDK - a toolkit for scalable, parallel visualization software
on shared memory supercomputers. He received his masters degree in Computer
Science from EPFL in 2015, and his Engineering Diploma in Computer Science in
1998. He is currently working towards a PhD in Computer Science at the
Visualization and MultiMedia Lab at the University of Zurich.
\end{IEEEbiography}

@@

\bibliographystyle{abbrv}
\bibliography{references}

>>>>

@@

% biography section
%
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)

\begin{IEEEbiography}[{
\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/stefan}}]{
Stefan Eilemann} Stefan is the technical manager of the Visualization Team in
the Blue
Brain Project. His work involves working towards large-scale visualization for
Exascale simulations; interactive integration of simulation, analysis and
visualization as well as flexible frameworks for data sharing and dynamic
allocation of heterogenous resources. He is the CEO and founder of Eyescale and
also the lead developer of the \textsf{Equalizer} parallel rendering framework.
He has worked in SGI's Advanced Graphics Division as the technical lead of
OpenGL Multipipe SDK - a toolkit for scalable, parallel visualization software
on shared memory supercomputers. He received his masters degree in Computer
Science from EPFL in 2015, and his Engineering Diploma in Computer Science in
1998. He is currently working towards a PhD in Computer Science at the
Visualization and MultiMedia Lab at the University of Zurich.
\end{IEEEbiography}

@@

\bibliographystyle{abbrv}
\bibliography{references/references}
